---
title: "Megatrends - Buzzwords"
author: "Alana Lane"
date: "28 June 2016"
output: html_document
---

This is a test document for Megatrends dashboard interface with R Markdown for BUZZ WORDS
Run the following line to return twitter token :
```{r bw_authority}

source("Collect/Authenticate/AuthenticateWithTwitterAPI.R")

```

Libraries
```{r bw_library}

library(twitteR)
library(tm)
library(wordcloud)
library(RColorBrewer)
library(ggplot2)
library(SnowballC)
library(RColorBrewer)
library(shiny)
library(devtools)
library(stringr)
library(RCurl)
library(XML)
library(bitops)
library(NLP)

```
Collect tweets containing 'Uni_Newcastle'
-Extract text content of all the tweets
-In tm package, the documents are managed by a structure called Corpus
-Create a term-document matrix from a corpus 
-ENTER STOP WORDS FILTER
-Convert as matrix tw_m
-Get word counts in decreasing order
-Create data frame with words and their frequencies
-Plot wordcloud
-ave the image in png format
-Make the wordcloud drawing predictable during a session

```{r bw_buzzwords}

word_tweets = searchTwitter("Uni_Newcastle", n=100, lang="en")
word_text = sapply(word_tweets, function(x) x$getText())
tw_words = Corpus(VectorSource(word_text))
tw_tdm = TermDocumentMatrix(tw_words,
                            control = list(removePunctuation = TRUE,
                                           stopwords = c("http", "amp", "httpstco.", "https", "httpstco..", "httpstco...", "Newcastle", "UniNewcastle", "Uni", "uni","text", "url", "file", "that", "all", "from", "has","was", "yes", "for", "and", "the", "that", "this", stopwords("english")),
                                           removeNumbers = TRUE, tolower = FALSE))


tw_m = as.matrix(tw_tdm)
word_freqs = sort(rowSums(tw_m), decreasing=TRUE) 
tw_dm = data.frame(word=names(word_freqs), freq=word_freqs)
head(word_freqs, 10)



wordcloud(tw_dm$word, max.words = 100, tw_dm$freq, random.order=FALSE, colors=brewer.pal(7, "YlGnBu"))
png("Collect/words/UONCloud.png", width=12, height=8, units="in", res=300)
wordcloud(tw_dm$word, max.words = 100,  tw_dm$freq, random.order=FALSE, colors=brewer.pal(7, "YlGnBu"))
dev.off()
wordcloud_rep <- repeatable(wordcloud)

```
```

