---
title: "Megatrends - Neg / Pos Sentiment"
author: "Alana Lane"
date: "28 June 2016"
output: html_document
---

This is a test document for Megatrends dashboard with R Markdown for NEG / POS SENTIMENT
Run the following line to return facebook public information -get user with token :
```{r np_authority}
library(RCurl)
library(Rfacebook)
library(ROAuth)
library(plyr)
library(stringr)
library(dplyr, pos=99) # dplyr and igraph in high position to avoid masking plyr.
library(igraph, pos=100)
library(magrittr)

fb_oauth = 'EAAO2eB6VThoBAOTnsBQwhe86oEpYQVZBtmDZAcJ7TvECpQFVq34csJtG0gLZBQWSSM4Mn4iqXjtUrHQnIHauJkKjkYoSmqWAPaZBlLhqSIIQZAZChLR5db72SyYKdNPREFF7bbc0YcWuxZAYWV1F8RbzospKWOwLb8ZD'
getUsers("me", token=fb_oauth, private_info=TRUE)

```

Get names of returned columns
Take a peek at the data
script for pos/neg sentiment 
Read negative and positive words from text file
what sort of words are "positive" or "negative".
Test the Score -Get score in rows and coloms for all posts
return string value
return types -create columns to combine score -Assign row count for neg pos values
create pie chart
```{r np_sentiment}

uon.page.df <- getPage("TheUniversityofNewcastleAustralia", token=fb_oauth, n=100, since=NULL, until=NULL, feed=TRUE)
names(uon.page.df) 
glimpse(uon.page.df) 
source("Collect/ref/sentiment.r")
pos <- readLines("Collect/ref/positive_words.txt") # Positive words
neg <- readLines("Collect/ref/negative_words.txt") # Negative words
sample(pos, size=10)
sample(neg, size=10)
uon.ss <- score.sentiment(sentence  = uon.page.df$message, 
                          pos.words = pos,        
                          neg.words = neg)$score  

uon.ss   <- score.sentiment(uon.page.df$message, pos, neg, .progress = 'text')
class(uon.ss)
uon.ss$score

st.err <- function(x){
  return(sd(x) / sqrt(length(x)))
}

uon.ss[c(1), 'score']
uon.ss$positive = uon.ss$score > 0
uon.ss$negative = uon.ss$score <= 0
negCount <- count(uon.ss$score <=0)
posCount <- count(uon.ss$score > 0)
count(uon.ss$score >0)

pole <- c("Negative", "Positive")
pie(negCount$freq, posCount$freq, labels = pole, radius = 1.0, main = "POS / NEG Sentiment @ UON", rep(1), col = terrain.colors(5))

```


```

