---
title: "Megatrends-Dashboard"
author: "Alana Lane"
date: "28 June 2016"
output: html_document
---

Libraries
```{r ts_library}

library(RCurl)
library(Rfacebook)
library(ROAuth)
library(twitteR)

library(httr)
library(httpuv)
library(rjson)
library(DT)
library(dplyr)
library(data.table)
library(reshape2)
library(ggplot2)
library(gplots)
library(plotly)

```

This is a test document for Megatrends dashboard interface with R Markdown for BUZZ WORDS
Run the following line to return twitter and facebook tokens :
```{r ts_authority}

source("Collect/Authenticate/AuthenticateWithTwitterAPI.R")
fb_oauth = 'EAAO2eB6VThoBAOTnsBQwhe86oEpYQVZBtmDZAcJ7TvECpQFVq34csJtG0gLZBQWSSM4Mn4iqXjtUrHQnIHauJkKjkYoSmqWAPaZBlLhqSIIQZAZChLR5db72SyYKdNPREFF7bbc0YcWuxZAYWV1F8RbzospKWOwLb8ZD'
getUsers("me", token=fb_oauth, private_info=TRUE)

```
-Get N number of posts from facebook and set table uon_page```
-Get N number of tweets from Twitter and set table tw_tweets
-save to data frame
-Create data table for colums likes_count, shares_count, comments_count
-load facebook data table uon_page
-Pull collumns
-view fb result if required
-Create data table for colums favoriteCount, retweetCount
-open data table tw_tweets
-gcreate table tw_resultsand add colums 3 and 12
-view TW result if required
-Merge table for output ts_result
```{r top_source}

uon_page <- getPage(page = "TheUniversityofNewcastleAustralia", token = fb_oauth, n = 100)
tw_timeline <- userTimeline('Uni_Newcastle', n=100)
tw_tweets <- twListToDF(tw_timeline)

datatable(head(uon_page), class = 'cell-border stripe')
fb_result = uon_page[ , c( 8, 10)]
head(fb_result)

datatable(head(tw_tweets), class = 'cell-border stripe')
tw_result = tw_tweets[ , c( 3, 12)]
head(tw_result)

ts_result = merge(fb_result, tw_result)
head(ts_result)

ts_m = as.matrix(ts_result)

counts <- table(ts_m)
head(counts)

my_cols <- c("darkblue", "yellow", "green", "lavender")
barplot(ts_m, space = 1.5, axisnames = TRUE, col = my_cols, legend = colnames(ts_m), ylim = c(0, 100000))


```


